---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DFOsalmonids

<!-- badges: start -->
[![R-CMD-check](https://github.com/poissonconsulting/DFOsalmonids/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/DFOsalmonids/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

DFOsalmonids is a data package containing salmon catch and release data ("salmonids") and example data for salmon counts by age class ("scale_data") provided by Fisheries and Oceans Canada (DFO).

## Installation

DFOsalmonids can be installed from GitHub using the remotes package:
``` r
# install.packages("remotes")
remotes::install_github("poissonconsulting/DFOsalmonids")
```

## Example

Loading in data for use:

``` {r, include = TRUE}
library(DFOsalmonids)
```

Viewing column (variable) names:

``` {r, include = TRUE}
colnames(salmonids)
colnames(scale_age)
```

Viewing the first few rows of 'scale_age' data:

``` {r, include = TRUE}
head(scale_age)
```

Viewing the first few rows of a subset from 'salmonids' data (only viewing several of the many columns/variables):

``` {r, include = TRUE}
salmonids[c(
  "SPECIES_NAME",
  "BROOD_YEAR",
  "START_DATE",
  "END_DATE",
  "TotTagged",
  "TotRelease",
  "Age",
  "TotCatch"
)] |>
  head()
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/DFOsalmonids/issues).

[Pull requests](https://github.com/poissonconsulting/DFOsalmonids/pulls) are always welcome.

## Code of Conduct

Please note that the DFOsalmonids project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.
